Holomorphic field theories and higher algebra

### 2022-09-29 draft.tex
small changes i hadnt saved

\begin{rmk}
Beilinson and Drinfeld introduced the notion of factorization algebras in their work on chiral conformal field theory \cite{BD},
and their version has had great success in algebraic geometry and representation theory,
particularly in the setting of the geometric Langlands program.
Gaitsgory, Francis, and Lurie ported the spirit of this notion into the setting of smooth manifolds,
developing topological chiral homology \cite{LurieHA} and factorization homology \cite{AF}
for questions in algebraic topology.
Motivated by all this work, Kevin Costello and the first author developed a version that works well for a broad class of quantum field theories and for more differential-geometric settings~\cite{CG1,CG2}.
\end{rmk}

@@

On the other hand, there is an open locus where the moduli stacks are equivalent:
the semi-stable points of $V/G$ \owen{fix description, as it's possibly just the stable locus}.
This locus determines the space $V//G$ and hence we have the isomorphism desired.
Let us try to unravel what this equivalence means for the field theories, both classical and quantum.

Consider any semistable point $x$ in $V/G$.
We view $x$ as a vacuum, which thus labels a perturbative classical theory describing the behavior of the theory $\cT$ near $x$ in the space of fields. 
For the vacuum $x$, the perturbative theory is equivalent to a holomorphic $\sigma$-model into the tangent space $T_x (V//G)$ \owen{Elaborate}. 
Hence the isomorphism of moduli spaces assures us there is a dual vacuum $x_D$ to $x$ in the dual theory, and its perturbative theory is equivalent to the perturbative theory for $x$
because there is an explicit identification of the tangent space to the corresponding point in the moduli space of the dual theory.
Thanks to this identification, a quantization of the theory labelled by $x$ determines a quantization of the theory labelled by $x_D$.
Hence on the semistable locus of $V/G$, we can guarantee an equivalence of quantizations.

>>>>

\begin{rmk}
Beilinson and Drinfeld introduced the notion of factorization algebras in their work on chiral conformal field theory \cite{BD},
and their version has had great success in algebraic geometry and representation theory,
particularly in the setting of the geometric Langlands program.
Gaitsgory, Francis, and Lurie ported the spirit of this notion into the setting of  manifolds,
developing topological chiral homology \cite{LurieHA} and factorization homology \cite{AF}
for questions in algebraic topology.
Motivated by these efforts (and benefiting from conversations as those works were in progress), 
Kevin Costello and the first author developed a version that works well for a broad class of quantum field theories and for more differential-geometric settings~\cite{CG1,CG2}.
\end{rmk}

@@

On the other hand, there is an open locus where the moduli stacks are equivalent:
the semi-stable points of $[V/G]$ \owen{fix description, as it's possibly just the stable locus}.
This locus determines the space $V\Sslash G$ and hence we have the isomorphism desired.
Let us try to unravel what this equivalence means for the field theories, both classical and quantum.

Consider any semistable point $x$ in $[V/G]s$.
We view $x$ as a vacuum, which thus labels a perturbative classical theory describing the behavior of the theory $\cT$ near $x$ in the space of fields. 
For the vacuum $x$, the perturbative theory is equivalent to a holomorphic $\sigma$-model into the tangent space $T_x (V//G)$ \owen{Elaborate}. 
Hence the isomorphism of moduli spaces assures us there is a dual vacuum $x_D$ to $x$ in the dual theory, and its perturbative theory is equivalent to the perturbative theory for $x$
because there is an explicit identification of the tangent space to the corresponding point in the moduli space of the dual theory.
Thanks to this identification, a quantization of the theory labelled by $x$ determines a quantization of the theory labelled by $x_D$.
Hence on the semistable locus of $[V/G]$, we can guarantee an equivalence of quantizations.
